```{r datasharing,echo=F,message=F,fig.height=5,fig.width=10}
library(plyr)
source("procdata3.R")
infiles<-c("X2014.08.05datasharing.rda",
           "X2014.08.05Reproducible1.rda",
           "X2014.08.05Exploratory1.rda",
           "X2014.08.05Rprogramming.rda")
classnames<-c("datasharing","Reproducible1","Exploratory1","Rprogramming")
interesting=ldply(infiles,process3)   
interesting$class_session<-as.factor(interesting$class_session)
``
```{r message=FALSE}
#     load(infile)
#     source("create_classtable.R")
#     source("procdata3.R")
#     #str(c)
library(reshape2)
    classtotals<-interesting %.%
        select(coursename,created.relative,class_session) %.%
        group_by(coursename,created.relative,class_session)%.%
        arrange(coursename,class_session,created.relative)%.%
        mutate(dummy=1)%.%
        summarize(total=sum(dummy))%.%
        group_by(coursename,class_session)%.%
        mutate(running=cumsum(total))
    overalltotals<-interesting %.%
        select(created.relative,class_session) %.%
        group_by(class_session,created.relative)%.%
        arrange(class_session,created.relative)%.%
        mutate(dummy=1)%.%
        summarize(total=sum(dummy))%.%
        group_by(class_session)%.%
        mutate(running=cumsum(total))
    #here are names split up
    nl=c("j1","j2","j3","username","foldername")
    nstuff=colsplit(interesting$html_url,"/",nl)
    

plot1<-ggplot(classtotals,aes(x=created.relative,y=running))+
        geom_line(aes(group=class_session,col=class_session))+
        ggtitle(title)+
        xlab("time since start of class (days)")+
        ylab("running total of repos forked")+
        facet_grid(coursename~.)
    plot2<-ggplot(overalltotals,aes(x=created.relative,y=total))+
        geom_line(aes(group=class_session,col=class_session))+
        ggtitle(title)+
        xlab("time since start of class (days)")+
        ylab("repos forked per day")
#     #return (c(plot1,plot2))
#     print(plot1)
#     print(plot2)
#     #return(plot1)
#     }
```
```{r message=FALSE}
    for (infile in infiles) {
    process(infile)
}
```
